Instructions for developing new pages for the MarineOmics webpage

### 2024-02-22 FUN_02_DNA_methylation.Rmd
fixing references to photos

---
title: 'DNA Methylation Assessment'
subtitle: '*Yaamini Venkataraman*, *Kathryn Greiner-Ferris*, *Sam White*, and *Steven Roberts*'
bibliography: DRAFT_DNA_methylation/DNA-Methylation.bib
---

@@

```{r meth-bp, echo = FALSE, out.width = "70%", fig.align = "center"}
knitr::include_graphics("DRAFT_DNA_methylation/meth-bp-chart.png")
```

@@

```{r meth-ratio, echo = FALSE, out.width = "70%", fig.align = "center", fig.cap = "Frequency distribution of methylation ratios for CpG dinucleotides in oyster gill tissue. [@10.7717/peerj.215](#refs)"}
knitr::include_graphics("DRAFT_DNA_methylation/meth_ratio.png")
```

```{r meth-igv, echo = FALSE, out.width = "100%", fig.align = "center", fig.cap = "Screenshot from IGV. Bedgraph files are displayed. See below for code to create these file (File Conversion)"}
knitr::include_graphics("DRAFT_DNA_methylation/igv.png")
```

@@

```{r meth-vert, echo = FALSE, out.width = "70%", fig.align = "center", fig.cap= "Genome screenshots of methylation quantified in 2kb running windows over the first 3Mb of chromosome 1 zebrafish and mouse, and of the largest scaffold (NW_006890054.1) in elephant shark (doi: 10.12688/f1000research.11281.1)"}
knitr::include_graphics("DRAFT_DNA_methylation/vert_methyl_distr.png")
```

@@

```{r meth-summary, echo = FALSE, out.width = "100%", fig.align = "center"}
knitr::include_graphics("DRAFT_DNA_methylation/bismark-summary-report.png")
```

>>>>

---
title: 'DNA Methylation Assessment'
subtitle: '*Yaamini Venkataraman*, *Kathryn Greiner-Ferris*, *Sam White*, and *Steven Roberts*'
bibliography: FUN_02_DNA_methylation/DNA-Methylation.bib
---

@@

```{r meth-bp, echo = FALSE, out.width = "70%", fig.align = "center"}
knitr::include_graphics("FUN_02_DNA_methylation/meth-bp-chart.png")
```

@@

```{r meth-ratio, echo = FALSE, out.width = "70%", fig.align = "center", fig.cap = "Frequency distribution of methylation ratios for CpG dinucleotides in oyster gill tissue. [@10.7717/peerj.215](#refs)"}
knitr::include_graphics("FUN_02_DNA_methylation/meth_ratio.png")
```

```{r meth-igv, echo = FALSE, out.width = "100%", fig.align = "center", fig.cap = "Screenshot from IGV. Bedgraph files are displayed. See below for code to create these file (File Conversion)"}
knitr::include_graphics("FUN_02_DNA_methylation/igv.png")
```

@@

```{r meth-vert, echo = FALSE, out.width = "70%", fig.align = "center", fig.cap= "Genome screenshots of methylation quantified in 2kb running windows over the first 3Mb of chromosome 1 zebrafish and mouse, and of the largest scaffold (NW_006890054.1) in elephant shark (doi: 10.12688/f1000research.11281.1)"}
knitr::include_graphics("FUN_02_DNA_methylation/vert_methyl_distr.png")
```

@@

```{r meth-summary, echo = FALSE, out.width = "100%", fig.align = "center"}
knitr::include_graphics("FUN_02_DNA_methylation/bismark-summary-report.png")
```
